Current status and propsects of R-packages for the design of experiments

### 2021-08-01 paper/index.Rmd
paper folder

---
title: Current status and propsects of R-packages for the design of experiments
author:
  # see ?rjournal_article for more information
  - name: Emi Tanaka
    affiliation: Monash University
    address:
    - Monash University
    - Clayton campus, VIC 3800, Australia
    url: http://emitanaka.org/
    orcid: 0000-0002-1455-259X
    email:  emi.tanaka@monash.edu
abstract: >
    Re-running an experiment is generally costly and in some cases impossible due to limited resources, so the design of experiment plays a critical role in increasing the quality of experimental data.  In this article I describe the current state of the R-packages for the design of experiments through textual analysis and download trends. I discuss also the software design of widely utilised R packages in the field of experimental design and conclude with discussion of some future prospects for the field.
preamble: |
  % Any extra LaTeX you need in the preamble

@@

output: rticles::rjournal_article
---

@@

Figure \ref{fig:dlplots} suggests that the \CRANpkg{AlgDesign} followed by \CRANpkg{agricolae} are far more downloaded than any other DoE pacakges. It is worth noting that \CRANpkg{agricolae} imports \CRANpkg{AlgDesign} thus any download of \CRANpkg{agricolae} likely results also in a download of \CRANpkg{AlgDesign}.

@@

@@

## Helping info to get started

Introductory section which may include references in parentheses
[@R], or cite a reference such as @R in the text.

## Section title in sentence case

Let's check fi this works Figure \@ref(fig:Rlogo).

This section may contain a figure such as Figure \ref{fig:Rlogo}.

## Summary

This file is only a basic article template. For full details of _The R Journal_ style and information on how to prepare your article for submission, see the [Instructions for Authors](https://journal.r-project.org/share/author-guide.pdf).

### About this format and the R Journal requirements

`rticles::rjournal_article` will help you build the correct files requirements:

* A R file will be generated automatically using `knitr::purl` - see
https://bookdown.org/yihui/rmarkdown-cookbook/purl.html for more information.
* A tex file will be generated from this Rmd file and correctly included in
`RJwapper.tex` as expected to build `RJwrapper.pdf`.
* All figure files will be kept in the default rmarkdown `*_files` folder. This
happens because `keep_tex = TRUE` by default in `rticles::rjournal_article`
* Only the bib filename is to modifed. An example bib file is included in the
template (`RJreferences.bib`) and you will have to name your bib file as the
tex, R, and pdf files.

>>>>

---
title: Current status and propsects of R-packages for the design of experiments
author:
  - name: Emi Tanaka
    affiliation: Monash University
abstract: >
    Re-running an experiment is generally costly and in some cases impossible due to limited resources, so the design of experiment plays a critical role in increasing the quality of experimental data.  In this article I describe the current state of the R-packages for the design of experiments through textual analysis and download trends. I discuss also the software design of widely utilised R packages in the field of experimental design and conclude with discussion of some future prospects for the field.
preamble: |
  % Any extra LaTeX you need in the preamble

@@

output: 
  bookdown::html_document2:
    theme: paper
---

@@

Figure \ref{fig:dlplots} suggests that the \CRANpkg{AlgDesign} followed by \CRANpkg{agricolae} are far more downloaded than any other DoE packages. It is worth noting that \CRANpkg{agricolae} imports \CRANpkg{AlgDesign} thus any download of \CRANpkg{agricolae} likely results also in a download of \CRANpkg{AlgDesign}.

@@

An experiment involves running a number of steps:

1. Defining the hypothesis or question
2. Formulating methods to test hypothesis or answer question 
3. Planning the experimental protocol:
  * Determining experimental resources, 
  * specifying the data collection procedure,
  * constructing the experimental design layout, and
  * proposing a model for analysis.
4. Collect data 
5. Analyse data, interpret result and conclusion

@@
